\section{Geometric covers are formally \etale}
In this section we want to prove, that covering stacks are formally \etale.
\subsection{The \etale topology is saturated}
Let $P$ denote a closed dense proposition.
\begin{lemma}{\label{lemma:covOfEF}}
	An \etale-flat DM-stack that is $\lnot \lnot$-inhabited is covering.
\end{lemma}
\begin{proof}
	If $X$ is an \etale-flat geometric stack, we may choose a geometric atlas $W \to X$ with $W$ formally \etale + flat. Using that the fibers $W \to X$ are $\lnot \lnot$-inhabited, we have 
	\begin{align*}
		\lnot \lnot X &\to \lnot \lnot W \\
		&\to W \in \bT  ´\\
		&\to X \in \CS \\
	\end{align*}
\end{proof}
\begin{lemma}{\label{lemma:wfcover}}
	For $X \in EF$, $X \to X^P$ is a map fibered in weakly-flat stacks iff for any $x, y : X$, $(x = y)^P$ is \etale-flat.
\end{lemma}
\begin{proof}
	\begin{itemize}
		
		\item[$\leftarrow$]
		By descent for covering stacks we may only show this for the fiber over $\Delta x $ for some $x  : X$ (Indeed let $z : X^P$. Assume $\|\sum_x \Delta x = z \|_\bT$. By descent we may replace $z$ by $\Delta x$ for some $x : X$ ) 
		But then the fiber is $\sum_y (x = y)^P$, a $\sum$ of \etale-flat geometric stacks which is merely inhabited, hence covering.
		\item[$\rightarrow$]The fiber-inclusion over $\Delta x$ is $(\sum_{y : X} (x = y)^P) \to X$ as calculated above. By stability under finite limits of $\EF$ the fiber $(x = y)^P$ over $y$ is an \etale-flat geometric stack.
	\end{itemize}
\end{proof}
\begin{lemma}{\label{lemma:ETALE}}
	Let $X$ be \etale-flat geometric stack and $P$ a closed dense proposition. Then TFAE
	\begin{enumerate}
		\item $X^P \in \EF$.
		\item $X \to X^P$ is an $\EF$-cover, i.e. a map fibered in \etale-flat stacks. % for any cld $P$
		\item $X \to X^P$ is a geometric cover % for any cld $P$
		\item $\Delta(X) : X \to X^P$ is an equivalence. 
		\item For any \etale-flat geometric stack $W$ such that $\Delta(W)$ is an equivalence and for any geometric cover $W \to X$ , $W^P \to X^P$ is fibered in $\EF$-stacks.
		\item The same as 5 but 'exists $W$' instead of 'for all'.
		%		\item For any $F : X \to \CS$ such that $\Delta(\sum_{X} F)$ is an equivalence and any $x : X^P$, $\prod_p F(x_p)$ is $\bT$-merely inhabited.
	\end{enumerate}
\end{lemma}
\begin{proof}
	\	\begin{enumerate}
		\item [1 $\Rightarrow$ 2] $\EF$ is stable under finite limits
		\item [2 $\Rightarrow$ 3] \ref{lemma:covOfEF}
		\item [4 $\Rightarrow$ 3 $\Rightarrow$ 1] obvious
		\item [1 $\Rightarrow$ 4]  we do induction over the truncation level. Contractible types are okay. Now let $X$ be an \etale-flat geometric stack. It suffices to show that $X \to X^P$ is an embedding by assumption (3) and \ref{lemma:covM1Stacks}. As $X \to X^P$ is in particular a map fibered in weakly flat stacks, for any $x,y : X$, $(x=y)^P \in \EF$ by \ref{lemma:wfcover}. $x = y$ is an \etale-flat geometric stack of one truncation level lower, we may apply the induction hypothesis thus $x = y \to (x = y)^P = (\Delta X =_{X^P} \Delta Y)$ is an equivalence. This map is $\ap_\Delta$.
		\item [ 6  $\Rightarrow$ 2 $\Rightarrow$ 5 ] Let $W \to X$ be a geometric cover with $\Delta W$ beeing an equivalence. Consider the commutative diagram
		% https://q.uiver.app/#q=WzAsNCxbMCwwLCJXIl0sWzEsMCwiV15QIl0sWzEsMSwiWF5QIl0sWzAsMSwiWCJdLFszLDJdLFswLDEsIlxcc2ltIl0sWzAsM10sWzEsMl1d
		\[\begin{tikzcd}
			W & {W^P} \\
			X & {X^P}
			\arrow["\sim", from=1-1, to=1-2]
			\arrow[from=1-1, to=2-1]
			\arrow[from=1-2, to=2-2]
			\arrow[from=2-1, to=2-2]
		\end{tikzcd}\]
		As beeing fibered in \etale-flat geometric stacks is a local property of morphisms of geometric stacks, $W^P \to X^P$ is fibered in \etale-flat stacks iff $X \to X^P$ is an $\EF$-cover, which is condition 2.
		\item [$5 \Rightarrow 6$] just use the definition of $\EF$: $X$ admits an atlas with $\EF$-domain.
		
	\end{enumerate}
\end{proof}
%\begin{corollary}
%	Let $X : \EF$ . Then $\Delta X : X \to X^P$ is fibered in weakly-flat stacks, iff its its an embedding.
%\end{corollary}
%--------------
\begin{lemma}{\label{lemma:EFPropFet}}
	\etale-flat geometric propositions are formally \etale.
\end{lemma}
\begin{proof}
	Let $X$ be such a proposition.
	We may show, that $X$ is $\lnot \lnot$ stable, as $\lnot \lnot$-stable propositions are formally \etale. If we assume $\lnot \lnot X$, then $X$ is covering by \ref{lemma:covOfEF}, thus by \ref{lemma:covM1Stacks} its contractible.
\end{proof}
\begin{corollary}[of \ref{lemma:EFPropFet}.]
	Covering sheaves are formally unramified.
\end{corollary}
%---------
\begin{lemma}{\label{lemma:OpenIsSmooth}}
	The type of open propositons $\mathsf{OPEN}$ is smooth. 
\end{lemma}
\begin{proof}

	Apply \ref{lemma:SmoothMonoid} to the map into a magma
	\begin{align*} 
		R &\to (\mathsf{OPEN} , \lor) \\
		f &\mapsto \mathrm{isInv} f % (f_1) \lor \hdots \lor \mathrm{isInv} (f_n)
	\end{align*}´
\end{proof}



%\begin{proof}
%%	Let $x , y : X \in \CS \cap \Set$. 
%\end{proof}

The next lemma will follow also from the next subsection in which we prove more generally that all \etale flat geometric stacks are formally \etale.
\begin{lemma}{\label{lemma:schemeEFIsFEt}}
	Let $X$ be a scheme that is \etale-flat as a GS. Then $X$ is formally \etale.
\end{lemma}
\begin{proof}
	By \ref{lemma:ETALE} we may show, that $X \to X^P$ is an \etale-flat cover. 	As $X$ is unramified by \ref{lemma:EFPropFet}, $x_p = y$ is an open proposition depending on $p : P$. But as the type of open propositions is smooth we find an open proposition $Q$ such that $\forall p, (x_p = y) = Q$. Then, using that $Q$ is formally \etale, % open proposition,
	\[(\prod_{p} x_p = y) = (P \to Q) = Q\] %= \lnot P \lor Q 
	But $Q$ is an open proposition, hence a formally \etale + flat scheme, thus an \etale-flat geometric stack.		
	
\end{proof}

\begin{corollary}{\label{cor:EtaleSat}}
	The \etale topology is saturated.
\end{corollary}
\begin{proof}
	Every affine covering stack is a scheme that is \etale-flat as a GS, by \ref{lemma:schemeEFIsFEt} its formally \etale. Its also fppf by saturatedness of fppf.
\end{proof}
\subsection{Formally \etale subuniverses}
\begin{definition}{\label{lemma:FisFet}}
	A formally \etale subuniverse is a subtype $\bF \subset FET$, such that one of the following equivalent conditions is satisfied
	\begin{enumerate}
		\item  $\bF$ is formally \etale.
		\item $\bF$ is formally smooth
		\item For any $X : FET$, $X \in \bF$ is smooth.
	\end{enumerate}
\end{definition}
\begin{proof}
	Use that 	$FET$ is formally unramified.
	\begin{enumerate}
		\item [$2 \Leftrightarrow 3$] Study the fibers of $\bF \to FET$ and use that beeing formaly \etale is stable under finite limits.
		\item [$1 \Leftrightarrow 2$]  The map $\bF \to FET$ is an inclusion, thus $\bF$ is formally unramified.
	\end{enumerate}
	
\end{proof}


\begin{lemma}{\label{cor:SubUnivDepProdStable}}
	Let $S : P \to \bF$, Then $\prod_p S_p : 1 \to \mathsf{\bF}$ is the unique filler.
	%	In particular: Let $S : \Aff$, such that  for any closed dense $P \to S \in \mathsf{StdEt}$. Then for any such $P$, $S^P \in \mathsf{StdEt}$.
\end{lemma}

\begin{proof}
	note that there exists a unique filler $\tilde Y : 1 \to \bF$, as $\bF$ is formally \etale. On the other hand the filler $1 \to FET$ is given by $\prod_p Y_p$. But $\bF \hookrightarrow FET$ is an embedding.
	% https://q.uiver.app/#q=WzAsNCxbMCwwLCJQIl0sWzEsMCwiXFxiRiJdLFsyLDAsIkZFVCJdLFswLDEsIjEiXSxbMCwxLCJZIl0sWzEsMiwiIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJ0b3AifX19XSxbMCwzXSxbMywxLCJcXGV4aXN0cyEiLDEseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMywyLCJcXHByb2RfcCBZX3AiLDJdXQ==
	\[\begin{tikzcd}
		P & \bF & FET \\
		1
		\arrow["Y", from=1-1, to=1-2]
		\arrow[from=1-1, to=2-1]
		\arrow[hook, from=1-2, to=1-3]
		\arrow["{\exists!}"{description}, dashed, from=2-1, to=1-2]
		\arrow["{\prod_p Y_p}"', from=2-1, to=1-3]
	\end{tikzcd}\]\\
	
	
	
\end{proof}
\begin{prop}
	For any modality $\ci$, there is a formally \etale subuniverse cut out by the $\ci$-modal types $FET \cap \cU_{\ci}$
\end{prop}
\begin{proof}
	We only need to show that $FET \cap \cU_{\ci}$ is formally smooth. Here you use that $\ci$-modal types are stable by depedent products over arbitrary indexing types.
\end{proof}
\begin{example}{\label{lemma:FETSt}}
	The following form formally \etale subuniverses:
	\begin{itemize}
		\item 	The class $FET \cap \St$ of formally \etale \etale-stacks
		\item 	The class of \etale propositions, i.e. propositions that are formally \etale \etale-sheaves.
	\end{itemize}	
\end{example}

\subsection{Standart \etale}
If $A$ is an fp $R$-algebra, $\Alg_A$ denotes fp $A$- algebras.
\begin{definition}
	Let $A$ be a f.p. $R$ algebra. The type of standart \etale $A$-algebra $\mathsf{StdEtAlg}_A$ is the type of f.p. flat $A$-algebras which are merely of the form
	\[
	\left (A[X_1,\hdots,X_n] / (P_1,\hdots,P_m) \right)_G
	\]
	such that $\det (\mathrm{Jac}(P_1,\hdots,P_n))$ divides $G$ in $A[X_1,\hdots,X_n] / (P_1,\hdots,P_m) $. \\
	We define $\mathsf{StdEt}_R$ as the class of types which merely is of the form
	\[\Spec A_1 + \hdots + \Spec A_n\]
	for $A_1,\hdots,A_n : \mathsf{StdEtAlg}_R$.
%	 = \sum_{X : \Aff} X^R \in \mathsf{StdEtAlg}_R$.
\end{definition}
\begin{question}
	Is standart \etale stable under finite sums?
\end{question}

\begin{definition}
	Let $A : \Alg_R$.
	 The type of Presentations of f.p. algebras over $R$ is 
	\[
	\Pres_A = \sum_{n,m} A[X_1,\hdots,X_n]^m
	\]
	We have a presentation forgetting map 
	\begin{align*}
		\mathrm{fgt} :\Pres_A &\to \Alg_A \\
		(n,m, P_1,\hdots,P_m) &\mapsto A[X_1,\hdots,X_n] / (P_1,\hdots,P_m)
	\end{align*}

	 %, where $\fp_*$ denotes the chance of coefficients $\fp \otimes_R R[X_1,\hdots,X_n] : A[X_1,\hdots,X_n] \to R[X_1,\hdots,X_n]$. \\
	
\end{definition}
\begin{construction}
	For any map of $R$-algebras $A \to B$ there is an evident pushforward map on type of presentations, which we call by abuse of notation the same as on algebras:
	% https://q.uiver.app/#q=WzAsNCxbMSwwLCJcXFByZXNfQiJdLFswLDAsIlxcUHJlc19BIl0sWzAsMSwiXFxBbGdfQSJdLFsxLDEsIlxcQWxnX0IiXSxbMCwzXSxbMSwyXSxbMiwzLCJcXF8gXFxvdGltZXNfQSBCIl0sWzEsMCwiIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV1d
	\[\begin{tikzcd}
		{\Pres_A} & {\Pres_B} \\
		{\Alg_A} & {\Alg_B}
		\arrow["\_ \otimes_A B",dashed, from=1-1, to=1-2]
		\arrow[from=1-1, to=2-1]
		\arrow[from=1-2, to=2-2]
		\arrow["{\_ \otimes_A B}", from=2-1, to=2-2]
	\end{tikzcd}\]
	making the diagram commute. \\
	It is given 
	\begin{align*}
		{\Pres_A} \simeq \sum_{n,m} A[X_1,\hdots,X_n]^m &\to \sum_{n,m} A[X_1,\hdots,X_n]^m \otimes_A B \simeq {\Pres_B} \\
		(n,m,P) &\mapsto (n,m,P\otimes 1)
	\end{align*}	
\end{construction}
\begin{lemma}{\label{lemma:PolyRingSmooth}}
	\begin{itemize}
		\item For any $n$ the type $R[X_1,\hdots,X_n]$ is formally smooth.
		\item The type $\Pres_R$ is smooth.
	\end{itemize}
\end{lemma}

\begin{proof}
	The second point follows from the first by $\sum$-stability of formally smooth types, as $\bN$ is formally smooth. Let $n : \bN$.% The type $R[X_1,\hdots,X_n]$ is formally smooth. 
	However we can write it as a sequential union
	\[
	R[X_1,\hdots,X_n] = \bigcup_k R[X_1,\hdots,X_n]_{\le k}
	\]
	where $ R[X_1,\hdots,X_n]_{\le k}$ is the finite free $R$-submodule generated by monomials with degree $\le k$. In particular it is a smooth type. Conclude by \ref{lemma:SeqUnionSmooth}.
\end{proof}
\begin{prop}{\label{prop:StdEtDualityForQuotients}}
	Let $R \twoheadrightarrow A$ be a quotient algebra. duality for fp algebras restricts to a bijection
	\[
	\mathsf{StdEtAlg}_A \cong (\Spec A \to \mathsf{StdEtAlg}_R)
	\]
\end{prop}

\begin{proof}
	
	Duality enhances to a bijection for pointed algebras
	\[
	\Alg_{A,*} \to (\Spec A \to \Alg_{R,*})
	\]
	Moreover, flatness is preserved under duality by \ref{thm:FlatAffines}.
	Def: A pointed $A$-algebra $(B,G)$ admits an apropriate presentation, if there exists a presentation $B = R[X_1,\hdots,X_n] / (P_1,\hdots,P_n)$ such that $\det(Jac(P_1,\hdots,P_n))$ divides $G$ in $B$. \\

	Let $(B,G)$ be  a pointed $A$-algebra. We need to show, that $(B,G)$ admits an approriate presentation iff it admits that pointwise. \\
	\begin{itemize}
		\item 
	If $B,G$ admits an appropriate presentation $F$ %$
	, then for any $\fp: \Spec A$, $F \otimes_A \fp$ %R[X_1,\hdots, X_n] / (\fp_* P_1,\hdots,\fp_* P_n)$ 
	is an appropriate presentation of $B \otimes_A \fp$. \\
	%, where $\fp_*$ denotes the chance of coefficients $\fp \otimes_R R[X_1,\hdots,X_n] : A[X_1,\hdots,X_n] \to R[X_1,\hdots,X_n]$. \\
	\item Assume that for $\fp : \Spec A$ we merely find an appropriate presentation of $B \otimes_A \fp$ as an $R$-algebra. 	Denote the proposition $P \equiv \Spec A$. In particular we have a solid arrow commutative diagram
%  https://q.uiver.app/#q=WzAsNixbMSwwLCJcXFByZXNfUiJdLFsyLDAsIlxcQWxnX1IiXSxbMCwwLCJQIl0sWzAsMSwiMSJdLFsyLDEsIlxcQWxnX0EiXSxbMSwxLCJcXFByZXMgQSJdLFswLDFdLFsyLDBdLFsyLDNdLFsxLDQsIlxcXyBcXG90aW1lc19SIEEiXSxbMywwLCIoMSkiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMyw0LCJCIiwyLHsiY3VydmUiOjR9XSxbNSw0XSxbMCw1LCJcXF9cXG90aW1lc19SIEEiXSxbMyw1LCIoMikiLDIseyJsYWJlbF9wb3NpdGlvbiI6NDAsInN0eWxlIjp7ImJvZHkiOnsibmFtZSI6ImRhc2hlZCJ9fX1dXQ==
\[\begin{tikzcd}
	P & {\Pres_R} & {\Alg_R} \\
	1 & {\Pres A} & {\Alg_A}
	\arrow[from=1-1, to=1-2]
	\arrow[from=1-1, to=2-1]
	\arrow[from=1-2, to=1-3]
	\arrow["{\_\otimes_R A}", from=1-2, to=2-2]
	\arrow["{\_ \otimes_R A}", from=1-3, to=2-3]
	\arrow["{(1)}", dashed, from=2-1, to=1-2]
	\arrow["{(2)}"'{pos=0.4}, dashed, from=2-1, to=2-2]
	\arrow["B"', curve={height=24pt}, from=2-1, to=2-3]
	\arrow[from=2-2, to=2-3]
\end{tikzcd}\]

	 % we are given a map $P \to \Pres_R$  if $P$ then we merely find an appropriate presentation of $B$ as an $R$-algebra. 
	 By smoothness of $\Pres_R$ , we find (1) an actual presentation $F : \Pres_R$, which presents $B \fp$ whenever $\fp : P$. 
	 The other half of the diagram still commutes 	using \todocite
	 	\[B \equiv \prod_{\fp : P} B_\fp = (\Spec A \to \mathrm{fgt} F) = \mathrm{fgt} F \otimes_R A \]
	 We may use (2) the presentation $F \otimes_R A : \Pres_{A}$ of $B$ as an $A$ algebra.

%	= \mathrm{fgt} (F \otimes_R A)

	It remains to show, that $F \otimes_R A$ is an appropriate presentation of the $A$-algebra $(B,G)$. However this is encoded by divisibility in $B$ which can be checked on points of $\Spec B$ \ref{ex:Divisibility}. Each such a point allows us to assume $\Spec A$. % It holds pointwise because $(B_\bullet ; G_\bullet)$ was assumed to be pointwise appropriate.
		\end{itemize}
	
	%	First observe that every $ B : \mathsf{StdEt}_A$  admits some $
	%	A StdEt presentation is a finitely presented $R[X]$ algebra
	%	Write $X = \Spec A$.
	%	Let $B : X \to \mathsf{StdEt}_R$. By ZLC for $X$ we find a Zariski cover $X' \to X$ with
	%	\[
	%	\prod_{x: X'}  
	%	\]
\end{proof}

	 we call a type $X$ $P$-smooth, if $X \twoheadrightarrow X^P$. $P$-smooth types are stable under $\sum$ by the following diagram
% https://q.uiver.app/#q=WzAsNSxbMCwyLCIoXFxzdW1fe3ggOkF9IEJ4KV5QIl0sWzEsMiwiQV5QIl0sWzEsMSwiQSJdLFswLDEsIlxcc3VtX3t4IDpBfSAoQngpIF5QIl0sWzAsMCwiXFxzdW1fe3ggOiBBfSBCIHgiXSxbMCwxXSxbMiwxLCIiLDIseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XSxbNCwzLCIiLDIseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XSxbMywwLCIiLDEseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XSxbMywyXSxbMywxLCIiLDEseyJzdHlsZSI6eyJuYW1lIjoiY29ybmVyLWludmVyc2UifX1dLFs2LDgsIiIsMix7InNob3J0ZW4iOnsic291cmNlIjoyMCwidGFyZ2V0IjoyMH19XV0=
\[\begin{tikzcd}
	{\sum_{x : A} B x} \\
	{\sum_{x :A} (Bx) ^P} & A \\
	{(\sum_{x :A} Bx)^P} & {A^P}
	\arrow[two heads, from=1-1, to=2-1]
	\arrow[from=2-1, to=2-2]
	\arrow[""{name=0, anchor=center, inner sep=0}, two heads, from=2-1, to=3-1]
	\arrow["\ulcorner"{anchor=center, pos=0.125}, draw=none, from=2-1, to=3-2]
	\arrow[""{name=1, anchor=center, inner sep=0}, two heads, from=2-2, to=3-2]
	\arrow[from=3-1, to=3-2]
	\arrow[shorten <=9pt, shorten >=9pt, Rightarrow, from=1, to=0]
\end{tikzcd}\]
\begin{lemma}{\label{lemma:FlatForStdEtAlg}}
%	Let $\Spec A$ be formally smooth. 
	Let $P$ be closed dense. Let $A$ be a $P$-unramified $R$-algebra. Then $A$ beeing quasi flat is $P$-smooth. % If , then $A = \prod_{\fp : P} B_\fp$ is a flat $R/I$-algebra.
\end{lemma}
\begin{proof}
	$A$ is flat iff any strong syzygy is explained in $A$, i.e. if for any $L \in R^{1 \times n} , X \in A^{n \times 1}$ such that $L \neq 0$ and $L X = 0$, there merely is a term in
	\[
	\sum_{Y \in A^{m\times 1}} \{ G \in R^{n \times m} \ | \ (L G = 0) \} \times (G Y = X).\]	
	%Assume this type is $P$-merely inhabited. %
	Its enough to see, that this type is $P$-smooth.
	\begin{itemize}
		\item 	The type $A^m$ is even formally smooth, as $A$ merely admits a surjection out of a polynomial ring \ref{lemma:PolyRingSmooth}. \\
		\item The $R$-module $\{ G \in R^{n \times m} \ | \ (L G = 0) \} \simeq (L^\bot)^{\oplus m}$ is finite free, as $L \neq 0$, thus formally smooth. Here we denote the hyperplane  $L^\bot = \{X :  R^{n \times 1} \ | \ L X = 0 \}$.
		\item $G Y =_{A^{n \times 1}} X$ is $P$-smooth: $A^{n \times 1}$ is $P$-unramified, as $A$ is $P$-unramified .
	\end{itemize}
%	Thus we merely can extract $Y , G$ such that $L G = 0$. It remains to show $G Y = X$	
\end{proof}
\begin{example}
	Let $B : P \to \mathsf{QuasiFlatAlg}_R$. Then $A	\equiv  \prod_{\fp : P} B_\fp$ is quasi-flat as an $R$-algebra. As it is $P$-merely quasiflat, we only have to check $P$-unramifiedness. given $x , y :  \prod_{\fp : P} B_\fp$ , 
	\[(x = y)^P = \left(\prod_{\fp : P} x \fp = y \fp \right)^P = \prod_{\fp : P} x \fp = y \fp = (x = y)\]
\end{example}
\begin{lemma}[TODO FLATNESS]{\label{lemma:StdEtSm}}
	%Let $B : Alg_R$ be smooth. 
	Then $\mathsf{StdEt}_R$ is a formally \etale subuniverse. 
	 %Let $A$ be a finitely presented $R$-algebra. Then '$A$ beeing standart \etale $R$-algebra' is formally smooth. \\
	%	A Zariski cover of standart \etale is standart \etale.
\end{lemma}
\begin{proof}
	\begin{itemize}
		\item For any $A : \mathsf{StdEtAlg}_R$ , $\Spec A$ is formally \etale \todocite. Thus a standart \etale type, as a finite sum of formally \etale types, is formally \etale
		\item formally smoothness: Apply \ref{lemma:SmoothMonoid} to the map into a magma
		\begin{align*}
			 \mathsf{StdEtAlg}_R &\to (\mathsf{StdEt}_R , +) \\
			 A &\mapsto \Spec A
		\end{align*}
		So it remains to show, that $\mathsf{StdEtAlg}_R$ is smooth.			
		Let $I^2 = 0$.
		%Choose a presentation $A = R[X_1,\hdots,X_n] / (\tilde P_1,\hdots,\tilde P_m)$. Let $P_1,\hdots P_m$ denote the images in $R/I[X_1,\hdots,X_n]$.
		Let $\Spec  R/ I \to \mathsf{StdEtAlg}_{R}$. By \ref{prop:StdEtDualityForQuotients} This corresponds to a unique $\mathsf{StdEtAlg}_{R/I}$, where $B' = R / I \otimes_R B$. choose a presentation
		\[
		T = \left (R/I[X_1,\hdots,X_n] / (P_1,\hdots,P_m) \right)_G
		\]
		and some $H : R/I[X_1,\hdots,X_n] / (P_1,\hdots,P_m)$ such that  
		\[\det (\mathrm{Jac}(P_1,\hdots,P_n)) \cdot H = G.\] \\
		Then choose lifts $\tilde P_1, \hdots, \tilde P_m \in R[X_1,\hdots,X_n]$ of the $P_i$, then a lift 
		\[\tilde H : R[X_1,\hdots,X_n] / (\tilde P_1 , \hdots, \tilde P_n)\]
		of $H$. Then define 
		\[
		\tilde G :\equiv \det (\mathrm{Jac}(\tilde P_1,\hdots, \tilde P_n)) \cdot \tilde H
		\]
		I claim, that
		\[\hat T \equiv \left(R[X_1,\hdots,X_n]  / (\tilde P_1,\hdots,\tilde P_n) \right)_{\tilde G} \]
		is a standart \etale $R$-algebra such that $\hat T \otimes_R R/ I = T$. \\
		For this we only need to see flatness. For this define $\mathsf{StdEt'}_R$ just as $\mathsf{StdEt}_R$ but without the flatness condition. The proof that was given shows that $\mathsf{StdEt'}_R$ is a formally \etale subuniverse. Thus by \ref{cor:SubUnivDepProdStable}, The unique filler $\Spec \hat T$ is given by $\prod_p \Spec T_p$, which is not $\sum_p \Spec T_p = \Spec \prod_p T_p$ (you can set $\Spec T_p = 1$).
%		\[\prod_p \Spec T_p = \prod_p \Hom_R(T_p , R) -WRONG- \Hom_R(\prod_p T_p , R) = \Spec (\prod_p T_p)\] 
		%using that whenever $p : P$, we have $T_p =_{\Alg_R} (\prod_q T_q).$
		% \prod_p \Hom_R(T_p , R / I) = \prod_p \Hom_R(T_p , R) = 
		
		
		
		 which is flat by \ref{lemma:FlatForStdEtAlg} TODO
		%	It remains to construct a $R$-algebra homomorphism
		%	% https://q.uiver.app/#q=WzAsNCxbMCwwLCJCIl0sWzEsMCwiXFx0aWxkZSBUIl0sWzAsMSwiQiciXSxbMSwxLCJUIl0sWzIsM10sWzEsMywiIiwyLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzAsMl0sWzAsMSwiIiwyLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV1d
		%	\[\begin{tikzcd}
		%		B & {\tilde T} \\
		%		{B'} & T
		%		\arrow[dashed, from=1-1, to=1-2]
		%		\arrow[from=1-1, to=2-1]
		%		\arrow[two heads, from=1-2, to=2-2]
		%		\arrow[from=2-1, to=2-2]
		%	\end{tikzcd}\]
		%	For this you need the smoothness of $B$. Indeed from the map $\Spec \tilde T \to \Spec B^{\bD 1}$ we merely obtain map $\Spec \tilde T \to \Spec B$.
		% if $I = 0$ it coincides with the $R / I$-algebra we started with.
	\end{itemize}
\end{proof}
\begin{question}
	Let $P \to \mathsf{StdEt}_R$ correspond to some $B : \mathsf{StdEt}_{R / I}$. What is $\Spec {}_R B$ where we restricted scalars ?
\end{question}



%	It is formally unramified, as   \\
%	So it remains formally smoothness. 
%	Let $Y : \mathsf{StdEt}^P$, $R : \prod_p Y_p^2 \to \mathsf{EtProp}$ such that for all $p$,  $R_p$ is an $\mathsf{EtProp}$-valued equivalence relation fibered in $\bF$. \\
%	As $\mathsf{StdEt}$ is formally \etale, we find a unique $\tilde Y : \mathsf{StdEt}$ such that for all $p$, $\tilde Y = Y_p$. Then our relation transport to a term $\tilde R$ in the LHS
%	\[
%	\prod_p Y_p^2 \to \mathsf{EtProp} = (\prod_p \tilde Y^2 \to \mathsf{EtProp}) = (\tilde Y^2 \to \mathsf{EtProp}^P) = (\tilde Y^2 \to \mathsf{EtProp})
%	\]
%	Using that the type of etale propositions is formally \etale \ref{lemma:FETSt}. \\
%	One  can check, that $\tilde R$ is indeed an equivalence relation on $\tilde Y$. It remains to show, that the relation $\tilde R$ is fibered in $\bF$. for any fiber this holds $P$-merely, which is enough by assumption \ref{lemma:FisFet} on $\bF$, as the fibers are formally \etale .
%	More precisely: For this we calculate $\tilde Y = \prod_p Y_p$ and $\tilde R(y,y') = \prod_p R(y_p,y'_p)$. Let $y : \tilde Y$. 
%	The fiber is
%	\[
%	\sum_{y' : \tilde Y} \tilde R(y , y') = \sum_{y': \tilde Y} \prod_p R(y_p,y'_p) = \prod_p \sum_{y' : Y_p} R(y_p , y')
%	\]
%	which is a dependent product of fibers of $R$. So conclude by \ref{cor:SubUnivDepProdStable}.
%	%, the fiber is $P$-merely in $\bF$. By assumption the fiber is in $\bF$.
%\end{proof}
\subsection{\etale-flat stacks form a formally \etale subuniverse}

%\begin{lemma}{\label{lemma:FETUniv}}
%	Let $\bF$ be a formally \etale subuniverse contained in $\EF$. An $\EF$ stack is formally \etale if it merely admits a geometric $\bF$-cover with formally \etale domain.
%\end{lemma}
%\begin{proof}
%
%\end{proof}


\begin{warning}
	$\EF \hookrightarrow \GS$ is probably not formally \etale.
\end{warning}
\begin{lemma}{\label{lemma:FetFromFCover}}
	An \etale-flat geometric stack is formally \etale , if it admits a geometric $\bF$-cover with formally \etale domain for $\bF$ some formally \etale subuniverse contained in $\EF$.
\end{lemma}
\begin{proof}
	Choose $f: W \to X$ a geometric $\bF$-cover with $W$ a formally \etale geometric stack. By \ref{lemma:ETALE}, we may show that $W \to X^P$ is an $\bF$-cover (thus an $\EF$-cover). The fiber over any $x :X^P$ is $\prod_p \fib_{f_p} x_p$ , a dependent product of things in $\bF$, thus in $\bF$ by \ref{cor:SubUnivDepProdStable}. 
\end{proof}
\begin{lemma}{\label{lemma:CSSubUniv}}
	Let $\bF \subset \EF$ be a formally \etale subuniverse. Then $\CS \cap \bF$ is a formally \etale subuniverse.
\end{lemma}
\begin{proof}
	As $\CS \cap \bF \subset \bF \subset FET$, we only need to show, that for any $ X: \bF$, $X \in \CS$ is formally smooth. But for some $X : \EF$ beeing $\lnot \lnot$ inhabited is formally smooth, so conclude by \ref{lemma:covOfEF}.
\end{proof}
\begin{lemma}{\label{lemma:ZarStdEtCover}}
	Every affine in the \etale topology merely admits a Zariski cover with domain in $\mathsf{StdEt}$
\end{lemma}
\begin{proof}
	 \todocite
\end{proof}
\begin{theorem}
	The type of $\EF$-stacks is a formally \etale subuniverse.
\end{theorem}
\begin{proof}
	By truncatedness of $\EF$-stacks we have $\EF = \bigcup_n \EF_n$, so by \ref{lemma:SeqUnionSmooth} we may just show, that $\EF_n$ form a formally \etale subuniverse for each $n$. 
	\begin{itemize}
		\item $n=0$: 
		%For $\bF$ be a formally \etale subuniverse, we call a sheaf a $\bF$-DM-sheaf if it is merely the quotient of some std\etale by an $\mathsf{EtProp}$-valued equivalence relation fibered in $\bF \cap \CS$.
		
		An algebraic space is called 
		\begin{itemize}
			\item 0-\etale-flat, if its Zariski-flat, i.e. merely a finite sum of open propositions: 
%			\[
%			\cP_{\Zar} \equiv \bigcup_n \mathsf{Open}^n % \{ X : \cU \ | \ \| \sum_{m : \bN} (Q : \mathsf{Fin} \ m \to \mathsf{Open}) \times X \simeq \sum_i Q i \| \}
%			\]
			%where we use the structure maps $X : \mathsf{Open}^n \mapsto (\bot , X) : \mathsf{Open}^{n+1}$
			\item $n+1$-\etale-flat, if it is merely the quotient of some std\etale by an $\mathsf{EtProp}$-valued equivalence relation fibered in $n$-\etale-flat covering algebraic spaces.
		\end{itemize}
		We have that $k$-\etale-flat algebraic spaces are \etale-flat geometric stacks by induction, using that $\mathsf{StdEt}$ is a subtype of formally \etale + flat affines.
		Observe that, the respective classes contain in particular
		\begin{enumerate}
			\item -\etale-flat algebraic spaces contain the \etale-topology \ref{lemma:ZarStdEtCover}.
			\item -\etale-flat algebraic spaces contains sheaves that merely admit an \etale-catlas $ S' \to F$, i.e. whose fibers as well as $S'$ belongs to the \etale topology. This is because by \ref{lemma:ZarStdEtCover} we can choose a Zariski cover $\mathsf{StdEt} \ni \hat S \to S'$ and then $\hat S \to S' \to F$ is still an \etale-cover. \\
			\item -\etale-flat algebraic spaces consists already of all $\EF$-algebraic spaces: Let $f : \Spec A \to X$ be a geometric atlas with $\Spec A$ beeing formally \etale + flat. We may assume that $\Spec A$ is standart \etale by \ref{lemma:ZarStdEtCover}. The equivalence relation $R$ on $\Spec A$ induced by $f$ is covering, thus its fibers merely admit an \etale-catlas by \ref{lemma:CovRel}. Hence $R$ is fibered in covering 2-\etale-flat algebraic spaces.
		\end{enumerate}
		We want to prove by induction, that $k$-\etale-flat algebraic spaces form a formally \etale subuniverse.
		\begin{itemize}
			\item  Zariski-Flat types form a formally \etale subuniverse. 
			\begin{itemize}
				\item Every finite sum of opens is formally \etale
				\item The type $\cP_{\Zar}$ is formally smooth: Apply \ref{lemma:SmoothMonoid} to the map into a magma $\mathsf{Open}  \to (\cP_{\Zar}, +)$.
				
			\end{itemize}
			\item For the induction step $n \mapsto n+1$:
			%For any formally \etale subuniverse $\bF$, the type of $\bF$-DM-sheaves is a formally \etale subuniverse.
			\begin{itemize}
				\item 	First we show that the type of $n+1$-\etale-flat algebraic spaces is formally smooth. Denote $\bF$ the covering $n$-\etale-flat algebraic spaces, which are a formally \etale subuniverse by the induction hypothesis and \ref{lemma:CSSubUniv}. Then the type of $n+1$-\etale-flat algebraic spaces admits a surjection out of 
				\[\sum_{X: \mathsf{StdEt}} (R : \mathrm{EqRel}(X  , \mathsf{EtProp})) \times (\prod_{x : X} R_x \in \bF) \]
				So it suffices to see, that this is formally \etale, which is a modality, thus its enough to see
					\begin{enumerate}
						\item $\mathsf{StdEt}$ is a formally \etale subuniverse by \ref{lemma:StdEtSm}
						\item $\mathsf{EtProp}$ is formally \etale subuniverse by \ref{lemma:EFPropFet}
						\item For any $x : X$, $R_x \in \bF$ is formally \etale: $R_x \equiv \sum_{y:X} R x y$ is formally \etale as $X$ is formally \etale by 1. and $R x y$ is by 2. So $R_x \in \bF$ is the fiber over $R_x$ of $\bF \to FET$, which is a map between formally \etale types.
					\end{enumerate}
				\item Every $n+1$-\etale-flat algebraic space admits a geometric cover fibered in $n$-\etale-flat algebraic spaces with formally \etale domain, thus it is formally \etale by the induction hypothesis and \ref{lemma:FetFromFCover}.
			\end{itemize}
		\end{itemize}
		\item $n \mapsto n+1$. By definition we need to show:
		\begin{itemize}
			\item Any \etale-flat geometric $n+1$-stack is formally \etale by \ref{lemma:FetFromFCover} using that \etale-flat geometric $n$-stacks are a formally \etale subuniverse by the induction hypothesis.
			\item To show $\EF_{n+1}$ beeing formally smooth, we may show \todocite that the domain of the surjection
			% https://q.uiver.app/#q=WzAsMyxbMCwwLCJcXHN1bV97WCA6IFxcU3QgXFxjYXAgRkVUfShYIFxcb3ZlcnNldHtGfXtcXHRvfSBcXENTX3tufSkgXFx0aW1lcyAoXFxzdW1fe1h9IEYgXFxpbiBcXEVGX24pIl0sWzEsMCwiXFxzdW1fe1ggOiBcXFN0IFxcY2FwIEZFVH0gWCBcXGluIFxcRUZfe24rMX0iXSxbMiwwLCJcXEVGX3tuKzF9Il0sWzAsMSwiIiwwLHsic3R5bGUiOnsiaGVhZCI6eyJuYW1lIjoiZXBpIn19fV0sWzEsMiwiIiwwLHsibGV2ZWwiOjIsInN0eWxlIjp7ImhlYWQiOnsibmFtZSI6Im5vbmUifX19XV0=
			\[\begin{tikzcd}
				{\sum_{X : \St \cap FET}(X \overset{F}{\to} \CS_{n}) \times (\sum_{X} F \in \EF_n)} & {\sum_{X : \St \cap FET} X \in \EF_{n+1}} & {\EF_{n+1}}
				\arrow[two heads, from=1-1, to=1-2]
				\arrow[Rightarrow, no head, from=1-2, to=1-3]
			\end{tikzcd}\]
			is formally \etale, where the right equality uses the previous paragraph. \\
			As beeing formaly \etale is a modality, we may only show that the following types are formally \etale
			\begin{itemize}
				\item $\St \cap FET$ by \ref{lemma:FETSt}
				\item $\CS_n$. It embeds into the formally \etale $\EF_n$ so conclude by \ref{lemma:CSSubUniv}.
				\item $\sum_X F \in \EF_n$. Here just use that the map $\EF_n \hookrightarrow \St \cap FET \ni \sum_X F$ between formally \etale types has formally \etale fibers.
			\end{itemize} 
		\end{itemize}
	\end{itemize}
\end{proof}
%\begin{proof}
%	Let $X : \GS$. Choose a geometric atlas $S \to X$. We have $S \in \EF$ iff $X \in \EF$. The first statement is formally \etale.
%\end{proof}
