
\section{Geometric propositions}
\begin{definition}
	$U : \Aff$ is called weakly-flat, if 
	\[\|U\|_\bT \to (U \in \bT)\]	
\end{definition}
\begin{lemma}{\label{lemma:geometricEquiv}}
	The converse holds always
\end{lemma}
\begin{proof}
	because things in $\bT$ are automatically $\bT$-merely inhabited
\end{proof}
\begin{example}
	Examples of weakly-flat affines for the Zariski topology
		\begin{itemize}
		\item finite sums of principal opens
		\item Closed propositions
	\end{itemize}
	for the fppf topology: flat affines . \\
	For the \etale topology: formally \etale affines
\end{example}

Recall the definition of $\bT$-atlas \ref{def:TAtlas}
\begin{definition}{\label{def:algprop}}
	Let $\bT$ be saturated. We call a modal proposition geometric, if one of the equivalent conditions is satisfied:
	\begin{enumerate}
		\item  its merely of the form $\|U\|_\bT$ for some geometric affine $U$.
		\item It is a geometric stack
%		\item There is a $\bT$-surjective map out of a geometric affine $U$.
		\item It has a $\bT$-atlas.

	\end{enumerate}
	
\end{definition}
\begin{proof} \
	\begin{enumerate}
		\item [1 $\Rightarrow$ 2]
		we show that $U \to \|U\|_\bT$ is a geometric atlas. Every fiber is in $\bT$, because $U$ is geometric. A $\bT$-atlas is a geometric atlas.
		\item [2 $\Rightarrow$ 3]
		If $P$ is a geometric -1-stack, then we may choose $U \to P$ a geometric atlas. This is a $\bT$-atlas by \ref{prop:affineCoveringStack}.

		\item [3 $\Rightarrow$ 1]
		
		Let $V \to P$ be a $\bT$-atlas.
		have to show TFAE $\|V\|_\bT \to P \to (V \in \bT) \overset{\ref{lemma:geometricEquiv}}{\to} \|V\|_\bT$. 
		Proof: $\|V\|_\bT \to P$ as $P$ is modal prop. Secondly, because $V \to P$ is a $\bT$-cover. \\
		Hence $P$ is a geometric proposition.
	\end{enumerate}
	
\end{proof}
\begin{lemma}{\label{lemma:covM1Stacks}}
	Even Without any saturatedness condition, Covering -1-stacks $X$ are contractible.
\end{lemma}
\begin{proof}
	Choose a geometric catlas $\bT \ni \Spec A \to X$. By the same trick as in the previous lemma, this induces an equivalence $1 \simeq \|\Spec A\|_\bT \overset{\sim}{\to} X$.
\end{proof}
\begin{example}
	Open / Closed Propositions are geometric.
\end{example}
\begin{question}
Is every geometric proposition a scheme?
\end{question}
It is an algebraic space that embeds into an affine, so it suffices to reproduce the statement from the presheaf model.

%\begin{lemma}[NECESSARY?]
%	geometric propositions are algebraic spaces.
%\end{lemma}
%\begin{proof}
%	We have $U \to \|U\|_\bT$ where $U$ is affine, hence an algebraic space and the fibers are in $\bT$ by geometricness of $U$, hence they are covering algebraic spaces. By stability under quotients, our geometric proposition is an algebraic space.
%\end{proof}
