\section{Local properties}

\begin{definition}
	Let $\cV \subset \cU$ a subclass of types be stable under finite limits. 
	We call a property $P$ of morphisms of types in $\cV$ $\bT$-local, if 
	\begin{enumerate}
		\item its satisfied by identities in $\cV$,
		\item stable under composition 
		\item
		Given a commutative triangle in $\cV$% https://q.uiver.app/#q=WzAsMyxbMCwwLCJYIl0sWzEsMCwiWSJdLFsxLDEsIloiXSxbMCwxLCJmIl0sWzEsMiwiZyJdLFswLDIsImgiLDJdXQ==
		\[\begin{tikzcd}
			X & Y \\
			& Z
			\arrow["f", from=1-1, to=1-2]
			\arrow["h"', from=1-1, to=2-2]
			\arrow["g", from=1-2, to=2-2]
		\end{tikzcd}\]
		with $X \to Y$ a geometric cover (wrt to $\bT$). Then $h$ has $P$ iff $g$ has $P$
		
	
	\end{enumerate}

\end{definition}
\begin{definition}
	$P$ has descent along geometric covers: Given $X,Y,Z,W \in \cV$. if $Y \to W$ is a geometric cover , then 
	% https://q.uiver.app/#q=WzAsNCxbMCwwLCJYIl0sWzAsMSwiWSJdLFsxLDEsIlciXSxbMSwwLCJaIl0sWzAsM10sWzAsMSwiZiciLDJdLFsxLDJdLFszLDIsImYiXSxbMCwyLCIiLDEseyJzdHlsZSI6eyJuYW1lIjoiY29ybmVyLWludmVyc2UifX1dXQ==
	\[\begin{tikzcd}
		X & Z \\
		Y & W
		\arrow[from=1-1, to=1-2]
		\arrow["{f'}"', from=1-1, to=2-1]
		\arrow["\ulcorner"{anchor=center, pos=0.125}, draw=none, from=1-1, to=2-2]
		\arrow["f", from=1-2, to=2-2]
		\arrow[from=2-1, to=2-2]
	\end{tikzcd}\]
	If $f$ has $P$ then $f'$ has $P$.
\end{definition}
	\begin{lemma}{\label{lemma:local}}
	If $P$ is local, then 
	\begin{itemize}
		\item geometric covers have P
		\item in descent, The statement 'If $f'$ has $P$ then $f$ has $P$' is automatic by Point 3.
	\end{itemize}
\end{lemma}
\begin{lemma}
	Beeing a geometric cover is local.
\end{lemma}
\begin{proof}
	Reduce to the case of $Z = 1$. If $X \to Y$ is a geometric cover, then $X$ is a covering stack iff $Y$ is a covering stack by stability under quotients and under sums. If both are coverings stacks, then the fibers 
\end{proof}

\begin{lemma}{\label{lemma:atlasOfMap}}
	Let $P$ be a local property of morphisms of geometric stacks. For
	A morphism between geometric stacks $f : X \to Y$  TFAE 
	\begin{enumerate}
		\item $f$ has $P$
		
		\item For any Atlas $\Spec A \to Y$ and any atlas $S \to X \times_Y \Spec A$ the composite $S \to \Spec A$ has $P$
		\item $f$ has an atlas that has $P$.
	\end{enumerate}
\end{lemma}
\begin{proof}
	\begin{itemize}
		\item [1 $\Rightarrow$ 2]
		Given a geometric atlas $\Spec A \to Y$ and taking the pullback % https://q.uiver.app/#q=WzAsNCxbMCwwLCJYIFxcdGltZXNfWSBcXFNwZWMgQSJdLFswLDEsIlgiXSxbMSwwLCJcXFNwZWMgQSJdLFsxLDEsIlkiXSxbMSwzLCJmIl0sWzAsMiwiZiciXSxbMiwzXSxbMCwxXV0=
		\[\begin{tikzcd}
			{X \times_Y \Spec A} & {\Spec A} \\
			X & Y
			\arrow["{f'}", from=1-1, to=1-2]
			\arrow[from=1-1, to=2-1]
			\arrow[from=1-2, to=2-2]
			\arrow["f", from=2-1, to=2-2]
		\end{tikzcd}\]
		$f'$ has $P$ as a basechange of $f$ along a geometric cover. Given a geometric atlas $S \to X \times_Y \Spec A$, it will have $P$, the composition $S \to \Spec A$ will be in $P$.
		\item [2 $\Rightarrow$ 3]
		$Y$ is a geometric stack, hence admits some geom atlas $\Spec A \to Y$. Again, $X \times_Y \Spec A$ is a geometric stack hence admits a geometric atlass.
		\item [3 $\Rightarrow$ 1]
		If we have an atlas $\tilde f : \tilde X \to \tilde Y$, then $\tilde X \to \tilde Y \to Y$ has $P$ by stability under composition. Then by (4) $X \to Y$ has $P$, as $\tilde X \to X$ is a geometric cover \\
		
	\end{itemize}
\end{proof}

So we may extend algebraic notions of maps to all geometric stacks:
\begin{definition}
	Let $P$ be a property of morphisms $\bT$-local in affine schemes.
	
	We define a morphism of geometric stacks $f : X \to Y$ to have $P$ iff
	there exist atlasses and a $P$-map on affines 
	% https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXFNwZWMgQSJdLFswLDEsIlgiXSxbMSwxLCJZIl0sWzEsMCwiXFxTcGVjIEIiXSxbMywyXSxbMCwxXSxbMSwyLCJmIiwxXSxbMCwzLCJcXGhhdCBmIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV1d
	\[\begin{tikzcd}
		{\Spec A} & {\Spec B} \\
		X & Y
		\arrow["{\hat f}", dashed, from=1-1, to=1-2]
		\arrow[from=1-1, to=2-1]
		\arrow[from=1-2, to=2-2]
		\arrow["f"{description}, from=2-1, to=2-2]
	\end{tikzcd}\]	
\end{definition}
\begin{lemma}
	Let $P$  be a local property of affine schemes. The induced property of morphisms of geometric stacks is local. Additionally descent is inherited.
\end{lemma}
\begin{proof}
	\begin{enumerate}
		\item Ok
		\item Ok
	
		\item geometric covers have $P$ and we have proven point 2., so one direction is clear.  Now assume 
		%https://q.uiver.app/#q=WzAsMyxbMCwwLCJYIl0sWzEsMCwiWSJdLFsxLDEsIloiXSxbMCwxLCJmIl0sWzEsMiwiZyJdLFswLDIsImgiLDJdXQ==
		\[\begin{tikzcd}
			X & Y \\
			& Z
			\arrow["f", from=1-1, to=1-2]
			\arrow["h"', from=1-1, to=2-2]
			\arrow["g", from=1-2, to=2-2]
		\end{tikzcd}\]
		Such that $f$ is a geometric cover and $h$ has $P$. \\
		We first reduce to the case where $Z$ is affine. Choose a geometric atlas $\tilde Z \to Z$. Then take the pullbacks
		% https://q.uiver.app/#q=WzAsNixbMiwwLCJcXHRpbGRlIFoiXSxbMiwxLCJaIl0sWzEsMCwiWSciXSxbMSwxLCJZIl0sWzAsMCwiWCciXSxbMCwxLCJYIl0sWzIsM10sWzMsMV0sWzAsMV0sWzIsMF0sWzIsMSwiIiwxLHsic3R5bGUiOnsibmFtZSI6ImNvcm5lci1pbnZlcnNlIn19XSxbNSwzXSxbNCw1XSxbNSwxLCJQIiwxLHsiY3VydmUiOjJ9XSxbNCwyXSxbNCwzLCIiLDEseyJzdHlsZSI6eyJuYW1lIjoiY29ybmVyLWludmVyc2UifX1dXQ==
		\[\begin{tikzcd}
			{X'} & {Y'} & {\tilde Z} \\
			X & Y & Z
			\arrow[from=1-1, to=1-2]
			\arrow[from=1-1, to=2-1]
			\arrow["\ulcorner"{anchor=center, pos=0.125}, draw=none, from=1-1, to=2-2]
			\arrow[from=1-2, to=1-3]
			\arrow[from=1-2, to=2-2]
			\arrow["\ulcorner"{anchor=center, pos=0.125}, draw=none, from=1-2, to=2-3]
			\arrow[from=1-3, to=2-3]
			\arrow[from=2-1, to=2-2]
			\arrow["P"{description}, curve={height=12pt}, from=2-1, to=2-3]
			\arrow[from=2-2, to=2-3]
		\end{tikzcd}\]
		$X' \to Y'$ is a geometric cover and By 3. $X' \to \tilde Z$ has $P$. \\
		So we may assume that $Z$ is affine. Then take a geometric atlas $\tilde X \to X$. The map $Y \to Z$ has the atlas $\tilde X \to X \to Z$ which has $P$ by stability under composition. Hence $Y \to Z$ has $P$.
			\item We show also descent: By \ref{lemma:local} we only need to show stability under basechange. Let $Z \to W$ have $P$, Given $Y \to W$ a geometric cover. We want to show that a basechagne $Y \times_W Z \to Y$ has $P$. The idea is to construct a common atlas of $Z \to W$ and its basechange. Choose an atlas $\tilde Y \to Y$. Then $\tilde Y \times_W Z \to Y \times_W Z$ is a geometric cover: It is a basechange of $\tilde Y \to Y$, because the outer diagram is a pullback
		% https://q.uiver.app/#q=WzAsNixbMCwwLCJcXHRpbGRlIFkgXFx0aW1lc19XIFoiXSxbMSwwLCJZIFxcdGltZXNfVyBaIl0sWzAsMSwiXFx0aWxkZSBZIl0sWzEsMSwiWSJdLFsyLDAsIloiXSxbMiwxLCJXIl0sWzAsMl0sWzAsMV0sWzIsM10sWzEsM10sWzMsNV0sWzEsNF0sWzQsNV0sWzEsNSwiIiwxLHsic3R5bGUiOnsibmFtZSI6ImNvcm5lci1pbnZlcnNlIn19XSxbMCwzLCIiLDEseyJzdHlsZSI6eyJuYW1lIjoiY29ybmVyLWludmVyc2UifX1dXQ==
		\[\begin{tikzcd}
			{\tilde Y \times_W Z} & {Y \times_W Z} & Z \\
			{\tilde Y} & Y & W
			\arrow[from=1-1, to=1-2]
			\arrow[from=1-1, to=2-1]
			\arrow["\ulcorner"{anchor=center, pos=0.125}, draw=none, from=1-1, to=2-2]
			\arrow[from=1-2, to=1-3]
			\arrow[from=1-2, to=2-2]
			\arrow["\ulcorner"{anchor=center, pos=0.125}, draw=none, from=1-2, to=2-3]
			\arrow[from=1-3, to=2-3]
			\arrow[from=2-1, to=2-2]
			\arrow[from=2-2, to=2-3]
		\end{tikzcd}\]
		Now choose any geometric atlas $S \to \tilde Y \times_W Z$. By composition this induce a map $S \to \tilde Y$: 
		It is both an atlas of the $P$-map $Z \to W$ and of $ Y\times_W Z \to Y$. So by \ref{lemma:atlasOfMap} $S \to \tilde Y$ has $P$ and thus $Y \times_W Z \to Y$ has $P$. 
		
	\end{enumerate}
\end{proof}
\subsection{Local properties of stacks}
\begin{definition}
	Let $\cV \subset \cU$ be a subclass of types stable under finite limits. A property $P$ of types in $\cV$ is local if 
	\begin{enumerate}
		\item $1 \in P$
		\item $P$ is $\sum$-stable
		\item If $X \to Y$ is a geometric cover between types in $\cV$, then $X$ has $P$ iff $Y$ has $P$.
		
	\end{enumerate}
	We say $P$ has descent if for all $X : \cV$, then $X$ having $P$ is a $\bT$-sheaf.
\end{definition}
\begin{lemma}
	Every local property of types in $\cV$ induces a local property of morphisms of types in $\cV$, by asking the property fiberwise.
\end{lemma}
\begin{proof}
	Use descent for the descent along a geometric cover ($\bT$-surjective!).
\end{proof}
\begin{lemma}
	Let $P$ be a $\sum$-stable-property of affines containg $\bT$. The induced property of geometric stacks is $\bT$-local.
\end{lemma}
\begin{proof}
	The $\sum$-stability is \ref{thm:atlasStableSum}. Covering stacks have $P$, as $\bT \subset P$. The quotient stability is straightforward.
\end{proof}
\subsection{Seperatedness}
\begin{definition}
Let $P$ be a $\bT$-local property of stacks.
We call a stack $P$-seperated, iff its identity types are $P$ stacks.
\end{definition}


\begin{lemma}{\label{lemma:SeperationIsLocal}}
	Let $P$ be a $\bT$-local property of stacks. Then beeing $P$-seperated is a $\bT$-local property %Then $\mathrm{Sep}(P)$ is local, defined as $X \in \mathrm{Sep}(P)$ iff $x = y$ has $P$ for all $x ,y : X$.
\end{lemma}
\begin{proof}
	Let $f : X \to Y$ be a geometric cover with $X$ beeing $P$-seperated. Let $x , y : Y$. Then by the construction in \ref{lemma:havingAbstractAtlasClosedUnderId} the map
	\[
	\fib_f x \times_X \fib_f y \to x = y
	\]
	is a geometric cover, whose domain has $P$ as $X$ is $P$-seperated and $P$ is stable under $\sum$. As $P$ is local, $x = y$ has $P$. \\
%	TODO Beeing $\bP$-seperated has descent.
\end{proof}
%
%\begin{example}
%	If $\cP$ is formally \etale, then beeing $\cP$-seperated means formally unramified.
%\end{example}
%\begin{lemma}{\label{lemma:SetUnramfied}}
%	Given morphisms of types $X \to Y \to Z$ with $X \to Z$ $\cP$-seperated and $Y$ a set, then $X \to Y$ is $\cP$-seperated.
%\end{lemma}
%\begin{proof}
%	We can argue fiberwise so we may assume $Z$ beeing the point. A fiber of $f : X \to Y$ over $y$ is $\sum_{x: X} f x = y$ where $f x = y$ is a proposition,hence $\cP$-seperated. As $X$ is $\cP$-seperated we conclude as $\cP$-seperated types are $\sum$-stable.
%\end{proof}

\begin{lemma}{\label{lemma:PImpliesPsep}}
	If $\sum$-stable property of affine schemes containing $\bT$ is stable under identity types, then the induced $\bT$-local property of geometric stacks is as well. %In this case the identity types of a $P$ stack have $P$ as well. \\	
\end{lemma}
\begin{proof}
	Let $X$ be a $P$ geometric stack. Let $x,y : X$ we want to show that $x =_X y$ has $P$. Choose a geometric atlas $P \ni S \overset{f}{\to} X$ . By assumption $S$ is $P$-seperated. We have a geometric atlas $\fib_f x \times_S \fib_f y \to x = y$. The domain is a $\sum$ of types in $\bT$ and identity types of $S$, which have $P$ by stability under identity types for the affine $S$. Hence $x = y$ has $P$. 
\end{proof}
\begin{lemma}{\label{lemma:FormEtaleSelfLocal}}
	If $Y \to X$ is a formally \etale $\bT$-surjective map between stacks and $Y$ is formally \etale, then $X$ is formally \etale.
\end{lemma}
\begin{proof}
	Take $L$ to be the modality which nullafies the propositions $\|\Spec A\|$ for $\Spec A$ \etale + fppf and all close dense propositions.
	The square 
	% https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXFNwZWMgQiJdLFsxLDAsIlxcU3BlYyBBIl0sWzAsMSwiRXQoXFxTcGVjIEIpIl0sWzEsMSwiRXQoXFxTcGVjIEEpIl0sWzEsM10sWzAsMiwiXFxzaW0iXSxbMiwzLCIiLDEseyJzdHlsZSI6eyJoZWFkIjp7Im5hbWUiOiJlcGkifX19XSxbMCwxXSxbMSwzXSxbMCwzLCIiLDEseyJzdHlsZSI6eyJuYW1lIjoiY29ybmVyLWludmVyc2UifX1dXQ==
	\[\begin{tikzcd}
		{Y} & {X} \\
		{L(Y)} & {L(X)}
		\arrow[from=1-1, to=1-2]
		\arrow["\sim", from=1-1, to=2-1]
		\arrow["\ulcorner"{anchor=center, pos=0.125}, draw=none, from=1-1, to=2-2]
		\arrow[from=1-2, to=2-2]
		\arrow[from=1-2, to=2-2]
		\arrow[from=2-1, to=2-2]
	\end{tikzcd}\]
	is a pullback as $L$ is lex. 
	We want to show, the right map is an equivalence. 
	Every type occuring is an \etale-stack.
	As the lower map is \etale-surjective, and the left vertical map is an equivalence, we can conclude.
\end{proof}
\begin{lemma}{\label{lemma:CSFEt}}
	Covering stacks are formally \etale.	
	%	If $\bT=$ \etale, then 
\end{lemma}
\begin{proof}
	We apply the recursion principle. Contractible types are formally \etale.
	If $\Spec B \to X$ is a formally \etale geometric cover  and $\Spec B \in \bT$  then $X$ is formally \etale by the previous lemma. % 
	
\end{proof}
\begin{lemma}{\label{lemma:FEtLocal}}
	formally \etale is an \etale-local property of geometric stacks.	
\end{lemma}
\begin{proof}
	geometric covers are formally \etale  by \ref{lemma:CSFEt}, so conclude by \ref{lemma:FormEtaleSelfLocal}
\end{proof}